Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-08-05 paper/ms.tex
update manuscript

\tn\ was observed by TESS from 26 March 2019 until 20 May 2019, during
the tenth and eleventh sectors of science operations
\citep{ricker_transiting_2015}.  The star was designated
TIC\,460205581 in the TESS Input Catalog
\citep{stassun_TIC_2018,stassun_TIC8_2019}.  Pixel data for an
$11\times11$ array surrounding the star were averaged and saved at
2-minute cadence.  The $2048\times2048$ image from the entire CCD was
also averaged into 30-minute stacks, and saved as a ``full frame
image'' (FFI).

The TESS project detected the transits in the 2-minute data and the
community was alerted on 17 June 2019.  Our subsequent blind search of
the CDIPS FFI light curves also showed the transits. Given that the
2-minute data had better sampling cadence, we opted to use the
Presearch Data Conditioning (PDC) light curve with the default
aperture for our
analysis~\citep{smith_kepler_2012,stumpe_multiscale_2014,jenkins_tess_2016,smith_finding_2016}.

@@

\clearpage
\acknowledgements
\raggedbottom

>>>>

\tn\ was observed by TESS from 26 March 2019 until 20 May 2019, during
the tenth and eleventh sectors of science operations
\citep{ricker_transiting_2015}.  The star was designated
TIC\,460205581 in the TESS Input Catalog
\citep{stassun_TIC_2018,stassun_TIC8_2019}.  Pixel data for an
$11\times11$ array surrounding the star were co-added and saved at
2-minute cadence.  The $2048\times2048$ image from the entire CCD was
also co-added into 30-minute stacks, and saved as a ``full frame
image'' (FFI).

The TESS Science Processing Operations Center
\citep{jenkins_tess_2016} processed the image data and identified the
transiting planet signature from two transits in
Sector 10, again with three transits in Sector 11, and then for a
final time when Sectors 1-13 were searched at the end of the first
year of the mission. The transit signature was fitted with a
limb-darkened transit model \citep{li_kepler_2019} and passed all the
diagnostic tests \citep{twicken_kepler_2018}, including the odd/even
depth test, the weak secondary eclipse test, the ghost diagnostic
test, and the difference image centroiding test, which placed the
transit source within $\sim$2 arcsec of the location of TOI~837. No
additional transit-like features were identified in any of the SPOC
searches. The TESS Science Office alerted the community to this
candidate transiting planet on 17 June 2019.  Our subsequent blind
search of the CDIPS FFI light curves also showed the transits. Given
that the 2-minute data had better sampling cadence, we opted to use
the Presearch Data Conditioning (PDC) light curve with the default
aperture for our
analysis~\citep{smith_kepler_2012,stumpe_multiscale_2014,smith_finding_2016}.

@@

%\clearpage
\acknowledgements
\raggedbottom
